Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-08-25 article/article.Rmd
Commit 2024-08-25 13:09

```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI."}
knitr::include_graphics("../images/P-relative-distribution-diff-1.png")
```

>>>>

```{r ovir-distribution, echo=FALSE, fig.cap="Relative frequency distribution of CE events in Thessaloniki for the period 1993 -- 2023 as a function of OI. The histogram was split in two plots with different y-axis scales for better readability."}
knitr::include_graphics("../images/P-relative-distribution-diff-2.png")
```
